Determinism, Complexity, and Predictability in Computer Performance

### 2014-07-16 related.tex
bunch of formatting issues
add comparison to boffetta

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities
between the two research projects.  Haven \emph{et al.} utilize the
relative entropy to quantify the difference in predictability between
two distributions: one evolved from a small ensemble of past states
using the known dynamical system, and the other the observed
distribution. Our work quantifies the predictability of a single
observed time series using weighted permutation entropy and makes no
assumptions about the generating process.  More closely related is the
work by Boffetta et al.~\cite{boffetta02}.  \alert{[[Sentences from
      Ryan explaining exactly what the difference is.]]]

>>>>

As a final note: there has been prior work under a similar title to
ours~\cite{haven2005}, but there are only superficial similarities between the
two research projects. Haven \emph{et al.} utilize the relative entropy to
quantify the difference in predictability between two distributions: one evolved
from a small ensemble of past states using the known dynamical system, and the
other the observed distribution. Our work quantifies the predictability of a
single observed time series using weighted permutation entropy and makes no
assumptions about the generating process. More closely related is the work by
Boffetta et al.~\cite{boffetta02}. There, they investigate the scaling behavior
of finite-size Lyapunov exponents (FSLE) and $\epsilon$-entropy for a wide
variety of systems. The scaling of these measures acts as a general proxy for
the theoretical ability to predict the future behavior of those systems. Though
in broad strokes our work is similar to theirs, it differs in two fundamental
ways. First, we consider with real-world data, e.g. stock prices, where we do
not necessarily have the ability to perturb or otherwise interact with the
system of interest, nor can we get an arbitrary amount of data which might be
needed to estimate the $\epsilon$-entropy for small $\epsilon$. Second, we tie
information, in the form of the weighted permutation entropy, directly to
prediction error via MASE values. Though FSLE and $\epsilon$-entropy allow for
the comparison of predictability between systems, they do not directly provide
an estimate of prediction error.
